---
output: html_document
---
#STAT 453 - Exam Notes
###By: Jordan Poles
http://odin.mdacc.tmc.edu/~yyuan/index_code.html
##Question 1
_Use a stoping size equal to cohort size!_

_Create your own  toxicity scenarios._
####Part 1

Here, I simulate the operating characteristics of a BOIN trial design given 5 different meaningful toxicity scenarios of my own design. I decided to take a slightly novel approach, and use procedural generation to describe several different toxicity scenarios using simple multivariate equations.

I've created a set of functions in R which make it simple to functionally compose a toxicity scenario using any bivariate equation (the results of which are automatically scaled from 0-1), and receive back both a plot of the toxicity scenario in 3D as well as a set of data points (a toxicity level for each level of treatment) which may be input directly into the BOIN R/GUI software in order to discretely simulate the scenario with a given set of drug concentrations. Additionally, the levels for each of the two drugs in question may be set, such that one increase in dosage is not necessarily as significant as a larger increase (or the relationship could be linear for each dosage step).

```{r, echo=FALSE}
library(BOIN)
library(ggplot2)
library(gridExtra)
library(plot3D)
f1 = function(i){(i["x"]+i["y"])}
f2 = function(i){(i["x"]+i["y"]**2)}
f3 = function(i){((i["x"]-3)**2-i["y"])}
#f4 = function(i){((i["x"])**2+.1*i["y"])}
f4 = function(i){((i["x"]+3)**4*(i["y"]+3)**4)}
f5 = function(i){((i["x"]-3)**2+(i["y"]-1)**2)}
plot_sim = function(fn, maxtox, name="fn", output=0){
  side = seq(1,4,.1)
  #side = c(1:4)
  siderange = c(min(side), max(side))
  xy = as.vector(expand.grid(side, side))
  colnames(xy) = c("x", "y")
  z = apply(xy, 1, fn)
  #scale 0 to 1
  z = scale(z, center = min(z), scale = max(z)-min(z))*maxtox
  ds = cbind(xy, z)
  z = matrix(z, ncol=length(side), byrow=TRUE)
  #p = plot_ly(z=~z) %>% add_surface() %>% layout(title=paste('Plot of', name))
  #p = ggplot(data=ds, aes(x=x, y=y, z=z))+geom_contour()
  if(output){
    persp3D(side, side, z, xlab="Gemcitabine Lvl", ylab="MK-8776 Lvl", main = paste('Plot of', name), zlim=c(0, 1))
  }
  return(ds)
}
side = c(1:4)
scenario_sim = function(fn, maxtox, xside=side, yside=side, output=0){
  xside = scale(xside, center = min(xside), scale = max(xside)-min(xside))
  yside = scale(yside, center = min(yside), scale = max(yside)-min(yside))
  xy = as.vector(expand.grid(xside, yside))
  colnames(xy) = c("x", "y")
  z = apply(xy, 1, fn)
  #scale 0 to 1
  z = scale(z, center = min(z), scale = max(z)-min(z))*maxtox
  ds = cbind(xy, z)
  z = matrix(z, ncol=length(yside), byrow=TRUE)
  if(output){
    persp(xside, yside, z, xlab="Gemcitabine Lvl", ylab="MK-8776 Lvl", zlim=c(0, 1))
  }
  return(z)
}
sims = c(f1, f2, f3, f4, f5)
names = c("f1", "f2", "f3", "f4", "f5")
outcomes = c()
scenarios = c()
for(i in seq_along(sims)){
  sim = sims[[i]]
  sim_name = names[i]
  outcome = plot_sim(sim, 1, sim_name, output=0)
  scenario = scenario_sim(sim, 1)
  scenarios = append(scenarios, list(scenario))
  outcomes = rbind(outcomes, cbind(outcome, i))
}
ggplot(data=outcomes, aes(x=x,y=y,z=z, colour=..level..))+geom_contour()+facet_wrap(~i)
```

A summary of our different toxicity scenarios:
```{r}
xside=c(400, 600, 800, 1000)
yside = c(20,40,80,112) 
```
1) A linear relationship with both drugs. Maxmimum toxicity when both drugs are at maximum. Here, and in the following scenarios, we assume that dosage levels are set such that 100% toxicity never occurs (we estimate max 80% toxicity).
```{r}
f1
maxtox=.8
ds = plot_sim(f1, maxtox, "Linear Relationship", 1)
scenario_sim(f1, maxtox, xside, yside, 1)
```

2) A linear relationship with Gemcitabine; quadratic growth with MK-8776 level. Maxmimum toxicity when both drugs are at maximum.
```{r}
f2
ds = plot_sim(f2, maxtox, "Linear Relationship", output=1)
scenario_sim(f2, maxtox, xside, yside, 1)
```

3)
```{r}
f3
ds = plot_sim(f3, maxtox, "Linear Relationship", output=1)
scenario_sim(f3, maxtox, xside, yside, 1)
```

4)
```{r}
f4
ds = plot_sim(f4, maxtox, "Linear Relationship", output=1)
scenario_sim(f4, maxtox, xside, yside, 1)
```

5)
```{r}
f5
ds = plot_sim(f5, maxtox, "Linear Relationship", output=1)
scenario_sim(f5, maxtox, xside, yside, 1)
```

Design
```{r}
get.oc.comb(.3, scenario_sim(f2, .8, xside, yside, 0), 42, 42, n.earlystop=NULL, startdose=c(1, 1), ntrial=1000, MTD.contour=FALSE)
```
####Part 2

Here we create a realistic phase 1 clinical trial scenario and

_We want to know if there are any dose transitions recommended by the software which look a bit fishy?_
##Question 2
_Set target toxicity probability (under target probability) to .25_

_Use the sample size stuff that's in there by default_

##Question 3
- You should be able to assign a drug quanity for each dosage level.
- You should be able to import/export curves as a CSV list.
